Schramm-Loewner evolution in tricritical Ising model

### 2013-06-27 AffineLieAlgebras/Simons/paper.tex
Some text on SLE and CFT (copy)

Consider following boundary condition:
\begin{equation}
  \label{eq:13}
  \underline{\begin{array}{llllllllll}
    & 3 & & 1 &  & 3 & - & 3 & & \\
    2 & & 2 &  & 2 & | & 4 & | & 2\\
    & 1 & & 3 & - & 3 & & 3 &- & \\
    2 & & 2 & | & 4 & & 4 & & 4\\
    &  3 & & 3 &- & 3 &- & 3 &- &\dots
  \end{array}}
\end{equation}
There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the

@@

>>>>

Consider following boundary condition:
\begin{equation}
  \label{eq:13}
  \underline{\begin{array}{llllllllll}
    & 3 & & 1 &  & 3 & - & 3 & & \\
    2 & & 2 &  & 2 & | & 4 & | & 2\\
    & 1 & & 3 & - & 3 & & 3 &- & \\
    2 & & 2 & | & 4 & & 4 & & 4\\
    &  3 & & 3 &- & 3 &- & 3 &- &\dots
  \end{array}}
\end{equation}
There is obviously an interface on double lattice delimiting $2$-s
from $4$-s. We need to prove conformal invariance of this interface.

@@

Connection of interfaces in restricted solid-on-solid models with
Schramm-Loewner evolution and conformal field theory was discussed in
the paper \cite{cardy2007ade}, but no rigorous proof was given.

In recent
years theoretical progress in the study of critical behavior was connected with the description of
geometrical objects -- interfaces. It was achieved by the use of
Scharmm-Loewner evolution \cite{schramm2000scaling}, which is
introduced as follows. 
Consider some critical lattice model on the upper half-plane
$\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$
(domain wall up to some length $t$). We denote this slit domain by
$\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$. Assume that
$\gamma_{t}$ satisfies restriction property and is conformally
invariant \cite{Cardy:2005kh}. Then conformal map
$g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential
equation \cite{schramm2000scaling}:
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

Sometimes it is more convenient to use the map $w_{t} (z)=g_{t}(z)-\sqrt{\kappa}\xi_{t}$, so the equation \eqref{eq:19} becomes
\begin{equation}
  \label{eq:20}
       d w _{t}= \frac{2dt}{w_{t} }-\sqrt{\kappa}d\xi_{t}  
\end{equation}

To establish the connection with conformal field theory one needs to
consider $N$-point correlation function of boundary CFT with boundary
condition changing operators $\varphi$ sitting at the tip of SLE trace
$z_t$ and at the infinity:
\begin{equation}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\}_{i=1}^{N})_{\mathbb{H}_{t}}=
\left<\varphi(z_{t}) \phi_{1}(z_{1},\bar z_{1}) \dots \phi_{n}(z_{n},\bar z_{n})
      \varphi(\infty)\right>,
    \label{eq:14}
\end{equation}
where $\phi_{i}$ are bulk primary fields with conformal weights $h_i$.
Then use the conformal map  $w(z):\mathbb{H}\setminus\gamma_{t}\to \mathbb{H}$ to rewrite expression \eqref{eq:14} in the whole upper half plane:
\begin{multline}
  \mathcal{F}(\left\{z_{i},\bar z_{i}\right\})_{\mathbb{H}_{t}}=\\
  =\prod \left(\frac{\partial w(z_{i})}{\partial z_{i}}\right)^{h_{i}} 
  \prod \left(\frac{\partial \bar w(\bar z_{i})}{\partial \bar z_{i}}\right)^{\bar h_i}
  \mathcal{F}(\left\{w_{i}, \bar w_{i}\right\})_{\mathbb{H}}
  \label{eq:4}
\end{multline}
To extend the definition of $\mathcal{F}$ to the whole plane we need
to double the number of fields $\phi_{i}$
\cite{cardy2004boundary,cardy1984conformal} and consider $w_{i},\bar
w_{i}$ as independent variables. For simplicity we will write
$\mathcal{F}(\left\{w_{i}\right\}_{i=1}^{2N})$.

Now we need to consider the evolution of SLE trace $\gamma_{t}$ from  $t$ to $t+ dt$. First factor in the right-hand-side of equation (\ref{eq:1}) gives us
\begin{equation*}
  -\frac{2h_{i}}{w_{i}^{2}}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}.
\end{equation*}
We denote by $\mathcal{G}_{i}$ the generator of infinitesimal
transformation of primary field $\phi_{i}$:$d\phi_{i}(w_{i}) =
\mathcal{G}_{i}\phi_{i}(w_{i})$:
 The generator of field transformation is equal to
\begin{equation}
  \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa} d\xi_{t}\right) \partial_{w_{i}}.
  \label{eq:11}
\end{equation}

The differential of $\mathcal{F}$ should be zero due to martingale condition.  Ito formula is used to calculate the differential. We need to include second order terms in  $\mathcal{G}_{i}$ since they contain squares of Brownian motion differential $d\xi_{t}$ with the expectation value proportional to $dt$ ($\mathbb{E}[d\xi_{t}^{2}]=dt$):
\begin{multline}
d \mathcal{F}_{\mathbb{H}_{t}}=\\ \left(\prod_{i=1}^{2N}\left(\frac{\partial w_{i}}{\partial z_{i}}\right)^{h_{i}}\right)
\left(-\sum_{i=1}^{2N}\frac{2h_{i}dt}{w_{i}^{2}}+\left[\sum_{i=1}^{2N}\mathcal{G}_{i}+\frac{1}{2}
      \sum_{i,j}\mathcal{G}_{i}\mathcal{G}_{j}\right]\right)\mathcal{F}_{\mathbb{H}}\\=0
\label{eq:8}
\end{multline}
Substituting  definition \eqref{eq:11} we get 
\begin{equation}
  \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa \mathcal{L}_{-1}^{2}\right)        \mathcal{F}_{\mathbb{H}}=0,
  \label{eq:4}
\end{equation}
with
\begin{eqnarray*}
  \mathcal{L}_{-n}=\sum_{i}\left(\frac{(n-1)h_{i}}{(w_{i}-z)^{n}}-\frac{\partial_{w_{i}}}{(w_{i}-z)^{n-1}}\right).
\end{eqnarray*}
This equation is equivalent to the algebraic condition on the boundary state $\varphi(0)\left|0\right>$:
\begin{multline}
  \label{eq:7}
  \left<0\left|\varphi(\infty)\phi_{1}(w_{1})\dots\phi_{2N}(w_{2N})
  \left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}\right)
\varphi(0)\right|0\right>=0.
\end{multline}
Since the set $\{\phi_{i}\}$ consists of arbitrary primary fields we conclude that 
\begin{equation}
|\psi>=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}\right)
\varphi(0)|0>
\end{equation}
is a null-state. Now act on $\psi$ by raising operators to get
equations connecting  $\kappa$, central charge $c$ and conformal
weight of boundary condition changing operator $h$.
\begin{eqnarray}
  \label{eq:15}
  c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}\\
  h=\frac{c}{3\kappa-8}
\end{eqnarray}

The behaviour of the dilute Ising and $A_4$ RSOS  models in tricritical
point is described by conformal field theory (CFT) with central charge $c=\frac{7}{10}$
\cite{friedan1985superconformal}.

We use CFT data to establish the value of Schramm-Loewner evolution parameter $\kappa$. The relation
$c=\frac{(8-3\kappa)(\kappa-6)}{2\kappa}$ gives us possible values of
$\kappa=\frac{16}{5},\; 5$. Boundary states satisfy Cardy conditions and were
classified by Chim \cite{chim1996boundary}. Conformal weights for the boundary fields are $h=0,\;
\frac{1}{10},\; \frac{3}{5},\; \frac{3}{2},\; \frac{3}{80},\;
\frac{7}{16}$.

Substituting $c=7/10, \kappa=16/5, 5$ in equations (\ref{eq:15}) we
obtain following possible values for conformal weight of boundary
condition changing operator: $h=7/16,1/10$

The model is also simplest example of supersymmetric conformal field theory. Schramm-Loewner
evolution on superspace was introduced in \cite{nagi2005stochastic,rasmussen2004stochastic}. The
relationship between the central charge and SLE parameter in this case is
$c=\frac{15}{2}-3\left(\kappa+\frac{1}{\kappa}\right)$. It gives us
$\kappa=\frac{3}{5},\frac{5}{3}$. (? c different for different sectors? )

We consider the model on the domain with a boundary (upper half-plane). So we need to impose
conformally invariant boundary conditions.
